EldersAIR: manuscript tables/figures

### 2021-12-15 manuscript_tables_figures.Rmd
minor updates for manuscript tables

# Summary stats for character/factor data
```{r}
# summary data for manuscript tables
char_funct_total <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  #filter(treatment_assigned == "Placebo") %>%
  #filter(area == "NPT") %>% 
  arrange(adult_id_char, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(adult_id_char, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = n()/total_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(new_var)
demographics_summary
}

char_funct_treatment <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  #filter(treatment_assigned == "Placebo") %>% 
  #filter(area == "NPT") %>% 
  arrange(adult_id_char, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(adult_id_char, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  mutate(total_n = n()) %>% 
  group_by(treatment) %>% 
  mutate(treatment_n = n()) %>% 
  group_by(treatment, new_var) %>% 
  mutate(n = n(),
         percent = n()/treatment_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(treatment, new_var)
demographics_summary
}

@@

char_funct_total("stove_age")
char_funct_treatment("stove_age")
char_funct_total("chimney_clean")
char_funct_treatment("chimney_clean")
char_funct_total("wood_collect_method")
char_funct_treatment("wood_collect_method")
char_funct_total("wood_collect")
char_funct_treatment("wood_collect")
char_funct_total("stove_grade")
char_funct_treatment("stove_grade")
char_funct_total("burn_level")
char_funct_treatment("burn_level")
```

# Summary stats for numeric data
```{r}
# summary data for manuscript tables - 1 response from Winter 1
num_funct_total <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  #filter(area == "NPT") %>% 
  filter(winter_id == 1) %>% 
  arrange(home, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(home, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  filter(!is.na(new_var)) %>% 
  dplyr::select(new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

num_funct_treatment <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>%
  #filter(area == "NPT") %>% 
  filter(winter_id == 1) %>% 
  arrange(home, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(home, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  filter(!is.na(new_var)) %>% 
  dplyr::select(treatment, new_var) %>% 
  group_by(treatment) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

# summary data for manuscript tables - averaged over multiple Winter 1 visits
num_funct_total <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  filter(area == "NN") %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  group_by(home, winter_id) %>% 
  mutate(mean_var = mean(new_var, na.rm = T)) %>% 
  ungroup() %>% 
  filter(winter_id == 1) %>% 
  arrange(home, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(home, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  filter(!is.na(mean_var)) %>% 
  dplyr::select(mean_var) %>% 
  summarize(mean_new_var = mean(mean_var), sd_var = sd(mean_var), n_var = n(), 
            min_var = min(mean_var), med_var = median(mean_var), max_var = max(mean_var))
demographics_summary
}

num_funct_treatment <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  filter(area == "NN") %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  group_by(home, winter_id) %>% 
  mutate(mean_var = mean(new_var, na.rm = T)) %>% 
  ungroup() %>% 
  filter(winter_id == 1) %>% 
  arrange(home, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(home, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  filter(!is.na(mean_var)) %>% 
  dplyr::select(treatment, mean_var) %>% 
  group_by(treatment) %>% 
  summarize(mean_new_var = mean(mean_var), sd_var = sd(mean_var), n_var = n(), 
            min_var = min(mean_var), med_var = median(mean_var), max_var = max(mean_var))
demographics_summary
}

@@

```{r}
pm_cutoff_table <- elders_cleaned_dataset_by_visit %>% 
  filter(!is.na(pm_mean_winter)) %>% 
  distinct(area, home, winter_id, .keep_all = T) %>% 
  mutate(epa_12 = if_else(pm_mean_winter > 12, "Above", "Below"),
         epa_35 = if_else(pm_mean_winter > 35, "Above", "Below")) %>% 
  group_by(winter_id, treatment, epa_35) %>% 
  count()
pm_cutoff_table
```

>>>>

# Summary stats for character/factor data
```{r}
# summary data for manuscript tables
char_funct_total <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  #filter(treatment_assigned == "Placebo") %>%
  #filter(area == "NPT") %>% 
  arrange(home, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(home, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = n()/total_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(new_var)
demographics_summary
}

char_funct_treatment <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  #filter(treatment_assigned == "Placebo") %>% 
  #filter(area == "NPT") %>% 
  arrange(home, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(home, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  mutate(total_n = n()) %>% 
  group_by(treatment) %>% 
  mutate(treatment_n = n()) %>% 
  group_by(treatment, new_var) %>% 
  mutate(n = n(),
         percent = n()/treatment_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(treatment, new_var)
demographics_summary
}

@@

char_funct_total("stove_age")
char_funct_treatment("stove_age")
char_funct_total("stove_cert")
char_funct_treatment("stove_cert")
char_funct_total("chimney_clean")
char_funct_treatment("chimney_clean")
char_funct_total("wood_collect_method")
char_funct_treatment("wood_collect_method")
char_funct_total("wood_collect")
char_funct_treatment("wood_collect")
char_funct_total("stove_grade")
char_funct_treatment("stove_grade")
char_funct_total("burn_level")
char_funct_treatment("burn_level")
```

# Summary stats for numeric data
```{r}
# summary data for manuscript tables - 1 response from Winter 1
num_funct_total <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  #filter(area == "NPT") %>% 
  #filter(winter_id == 1) %>% 
  arrange(home, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  filter(!is.na(new_var)) %>% 
  dplyr::select(new_var, winter_id) %>% 
  group_by(winter_id) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

num_funct_treatment <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>%
  #filter(area == "NPT") %>% 
  #filter(winter_id == 1) %>% 
  arrange(home, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  filter(!is.na(new_var)) %>% 
  dplyr::select(treatment, new_var, winter_id) %>% 
  group_by(winter_id, treatment) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

# summary data for manuscript tables - averaged over multiple Winter 1 visits
num_funct_total <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  #filter(area == "NN") %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  group_by(home, winter_id) %>% 
  mutate(mean_var = mean(new_var, na.rm = T)) %>% 
  ungroup() %>% 
  #filter(winter_id == 1) %>% 
  arrange(home, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  filter(!is.na(mean_var)) %>% 
  dplyr::select(winter_id, mean_var) %>% 
  group_by(winter_id) %>% 
  summarize(mean_new_var = mean(mean_var), sd_var = sd(mean_var), n_var = n(), 
            min_var = min(mean_var), med_var = median(mean_var), max_var = max(mean_var))
demographics_summary
}

num_funct_treatment <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  #filter(area == "NN") %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  group_by(home, winter_id) %>% 
  mutate(mean_var = mean(new_var, na.rm = T)) %>% 
  ungroup() %>% 
  #filter(winter_id == 1) %>% 
  arrange(home, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  filter(!is.na(mean_var)) %>% 
  dplyr::select(winter_id, treatment, mean_var) %>% 
  group_by(winter_id, treatment) %>% 
  summarize(mean_new_var = mean(mean_var), sd_var = sd(mean_var), n_var = n(), 
            min_var = min(mean_var), med_var = median(mean_var), max_var = max(mean_var))
demographics_summary
}

@@

```{r}
pm_cutoff_table <- elders_cleaned_dataset_by_visit %>% 
  filter(!is.na(pm_mean_winter)) %>% 
  distinct(treatment, home, winter_id, .keep_all = T) %>% 
  mutate(epa_12 = if_else(pm_mean_winter > 12, "Above", "Below"),
         epa_35 = if_else(pm_mean_winter > 35, "Above", "Below")) %>% 
  group_by(winter_id, treatment, epa_35) %>% 
  count()
pm_cutoff_table
```
